\LARGE Micro- versus meso-scale population models for ecological forecasting under climate change

### 2014-10-25 manuscript/ms_MicroMeso.Rnw
again updated caption.
updated affiliations

\title{\LARGE Micro- versus meso-scale population models for ecological forecasting under climate change}
\author[1]{\large Andrew T. Tredennick} 
\author[1]{\large Peter B. Adler}
\affil[1]{\footnotesize Department of Wildland Resources and the Ecology Center, Utah State University}
\maketitle

@@

\section{Selecting climate covariates}
For both the individual-level IPM (IPM) and the quadrat-based IBM (QBM) we followed the same model selection approach for including climate covariates in vital rate regressions.  Working within the random effects structure described previously, we fit a set of models with all possible combinations of four climate covariates: fall through spring precipitation at \emph{t}-1 and \emph{t}-2 (ppt1 and ppt2, respectively) and mean spring temperature at \emph{t}-1 and \emph{t}-2 (TmeanSpr1 and TmeanSpr2, respectively), where \emph{t} is the observation year. The combinations of climate covariates we fit included same-year interactions between precipitation and temperature (e.g., a ppt1$\times$TmeanSpr1 interaction). Finally, we also fit a model with no climate covariates included as fixed effects. In total, this resulted in a set of 25 candidate models.

@@

print(xtable(allTableQBM, align=c("l", "l", "l", "l", "l", "l", "X"), 
             caption="The proportion of interannual variability in  vital rates explained by the climate covariates. The contribution is defined as: (Climate model - Constant Model)/(Full model - Constant model). Note that in some cases this will be slightly negative where DIC selected a model with climate covariates but a model without climate covariates had a very similar DIC value."), 
      tabular.environment="tabularx", caption.placement="top",
      width="\\textwidth", include.rownames=FALSE)
@

>>>>

\title{\LARGE Micro- versus meso-scale population models for ecological forecasting under climate change}
\author[]{\large Andrew T. Tredennick} 
\author[]{\large Peter B. Adler}
\affil[]{\footnotesize \emph{Department of Wildland Resources and the Ecology Center, Utah State University}}
\maketitle

@@

\subsection{Selecting climate covariates}
For both the individual-level IPM (IPM) and the quadrat-based IBM (QBM) we followed the same model selection approach for including climate covariates in vital rate regressions.  Working within the random effects structure described previously, we fit a set of models with all possible combinations of four climate covariates: fall through spring precipitation at \emph{t}-1 and \emph{t}-2 (ppt1 and ppt2, respectively) and mean spring temperature at \emph{t}-1 and \emph{t}-2 (TmeanSpr1 and TmeanSpr2, respectively), where \emph{t} is the observation year. The combinations of climate covariates we fit included same-year interactions between precipitation and temperature (e.g., a ppt1$\times$TmeanSpr1 interaction). Finally, we also fit a model with no climate covariates included as fixed effects. In total, this resulted in a set of 25 candidate models.

@@

print(xtable(allTableQBM, align=c("l", "l", "l", "l", "l", "l", "X"), 
             caption="The proportion of interannual variability in  vital rates explained by the climate covariates. The contribution is defined as: (Climate model - Constant Model)/(Full model - Constant model). The values are residual deviance. Note that in some cases this will be slightly negative where DIC selected a model with climate covariates but a model without climate covariates had a very similar DIC value."), 
      tabular.environment="tabularx", caption.placement="top",
      width="\\textwidth", include.rownames=FALSE)
@
